Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-21 demystify.tex
updates

\part{Introduction To CS PhD Admission}\label{part:intro}

@@

\myepigraphsimpsons{``Son, if you really want something in this life, you have to work for it. Now quiet! They’re about to announce the lottery numbers.''}

@@

\myepigraphsimpsons{``To whom it may concern… D’oh!''}

@@

@@

@@

@@

@@

\chapter{Miscellaneous}\label{chap:misc}
\section{CV/Resume}
\sectioninfo{Highlight and summarize major achievements, e.g., Publications, Programming Awards}

@@

\section{Writing Sample}\label{sec:writing-sample}
It is a good idea to upload a writing sample, e.g., a paper you wrote, a report, or a thesis.  Even if the paper is published, not published, or already on Arxiv, you should upload it. Because samples are part of the application package, adcom members can quickly skim through it to see your research and writing abilities.

@@

\chapter{Dealing with Rejection}\label{chap:not-accepted}

@@

\part{Types of Funding and Choosing Schools and Profs.}\label{part:funding-schools-profs}

@@

\myepigraphsimpsons{``Bart, with \$10,000, we’d be millionaires! We could buy all kinds of useful things like ... love!''}

@@

\chapter{Choosing Schools and Professors}\label{sec:schoolsandprofs}

\chapterinfo{Not every university has a CS PhD program. Not every professor, even those in CS, can advise or graduate CS PhD students.}

\myepigraphsimpsons{``The answer to life's problems aren't at the bottom of a bottle. Heh heh! They're on TV!''}

@@

\begin{commentbox}[Hung:]
  I always encourage the students I admit to talk with my students and the students of other faculty in other schools who admitted them. You will unlikely hear straight-out complaints from current students in a prof’s group. But sometimes what is important are things that they (current students) don’t tell you. Pay attention to their ``level of excitement'' being in the group.
\end{commentbox}

@@

\section{Choosing an Adviser}
\sectioninfo{The best adviser is the one that you can work well with. But you do not know that until you start working with them.}

There is no one-size-fits-all answer to this question. The best adviser is the one that you can work well with.  But how do you find such a person?

@@

\subsection{Finding an Adviser}

@@

\subsubsection*{Additional Resources}
\begin{itemize}
  \item \href{https://www.cs.columbia.edu/wp-content/uploads/2019/03/Get-Advisor.pdf}{The Definitive ``what do I ask/look for'' in a PhD Adviser Guide}
\end{itemize}
\subsection{Who can serve as a PhD adviser?}\label{sec:faculty-types}

@@

\subsection{Tenured or tenure-track faculty?}\label{sec:tenure-vs-tenure-track}

@@

\myepigraphsimpsons{``I didn’t do it. Nobody saw me do it. You can’t prove anything!''}

@@

\myepigraphsimpsons{``I’m not a bad guy! I work hard, and I love my kids. So why should I spend half my Sunday hearing about how I’m going to Hell?''}

>>>>

\part{Introduction}\label{part:intro}

@@

\myepigraphsimpsons{``Son, if you really want something in this life, you have to work for it. Now quiet! They're about to announce the lottery numbers.''}

@@

\myepigraphsimpsons{``To whom it may concern… D'oh!''}

@@

\myepigraphsimpsons{``I've got to study harder and publish faster!''}

@@

\myepigraphsimpsons{``All my life I’ve had one dream: to achieve my many goals.''}

@@

\myepigraphsimpsons{``Woohoo! I'm a college man! I won't need my high school diploma anymore''}

@@

\myepigraphsimpsons{``I've got to study harder. Everyone knows standardized tests are biased against the poor, the lazy, and the stupid.''}

@@

\chapter{Miscellaneous}\label{chap:misc}

\myepigraphsimpsons{``I'm not a college graduate. I'm not even a high school graduate. But I'm a pretty good judge of character.''}

\section{CV/Resume}
\sectioninfo{Highlight and summarize major achievements, e.g., Publications, Programming Awards}

@@

\section{Writing Sample}\label{sec:writing-sample}
It is a good idea to upload a writing sample, e.g., a paper you wrote, a report, or a thesis.  Whether the paper is published, not published, or already on Arxiv, you should upload it. Because samples are part of the application package, adcom members can quickly skim through it to see your research and writing abilities.

@@

\chapter{Dealing with Rejection}\label{chap:not-accepted}
\chapterinfo{Rejection is common and part of academia.  Common reasons for rejection include aiming too high, not a good fit, or bad luck. Learn from it and try again.}

\myepigraphsimpsons{``You tried your best and you failed miserably. The lesson is: never try.''}

Rejection is a common part of the PhD application process.  In fact, rejection is part of academia (e.g., you will get rejected for papers, grants, jobs, etc).  Don't take rejection personally and to learn from it.

@@

\part{Funding, Schools, and Profs.}\label{part:funding-schools-profs}

@@

\myepigraphsimpsons{``Bart, with \$10,000, we'd be millionaires! We could buy all kinds of useful things like ... love!''}

@@

\chapter{Choosing Schools}\label{sec:schoolsandprofs}
\chapterinfo{Not every university has a CS PhD program. Not every professor, even those in CS, can advise or graduate CS PhD students.}

\myepigraphsimpsons{``It's not the school you go to, it's what you do while you're there!''}
%\myepigraphsimpsons{``The answer to life's problems aren't at the bottom of a bottle. Heh heh! They're on TV!''}

@@

\begin{commentbox}[Hung:]
  I always encourage the students I admit to talk with my students and the students of other faculty in other schools who admitted them. You will unlikely hear straight-out complaints from current students in a prof's group. But sometimes what is important are things that they (current students) don't tell you. Pay attention to their ``level of excitement'' being in the group.
\end{commentbox}

@@

\chapter{Choosing an Adviser}\label{chap:choosing-adviser}
\chapterinfo{The best adviser is the one that you can work well with. But you do not know that until you start working with them.}

There is no one-size-fits-all answer to finding an adviser. The best adviser is the one that you can work well with.  But how do you find such a person?

@@

\section{Finding an Adviser}

@@

\subsection*{Additional Resources}
\begin{itemize}
  \item \href{https://www.cs.columbia.edu/wp-content/uploads/2019/03/Get-Advisor.pdf}{The Definitive ``what do I ask/look for'' in a PhD Adviser Guide}
\end{itemize}

\section{Who can serve as a PhD adviser?}\label{sec:faculty-types}

@@

\section{Tenured or tenure-track faculty?}\label{sec:tenure-vs-tenure-track}

@@

\myepigraphsimpsons{``I didn't do it. Nobody saw me do it. You can't prove anything!''}

@@

\myepigraphsimpsons{``I'm not a bad guy! I work hard, and I love my kids. So why should I spend half my Sunday hearing about how I'm going to Hell?''}
